The Rockerverse: Packages and Applications for Containerisation with R

### 2020-03-12 rockerverse.Rmd
fix contribution by @thebioengineer
See https://github.com/nuest/rockerverse-paper/issues/26#issuecomment-597935834

The ordering of authors following DN and DE is alphabetical.
DN conceived the article idea, \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}, wrote sections not mentioned below, and revised all sections.
DE wrote the introduction and the section about containerisation and the Rocker Project, and reviewed all sections.
DB wrote the section on \pkg{outsider}.
GD contributed the CARD.com use case.
RC \& EH contributed to the section on interfaces for Docker in R (_dynverse_ and `dynwrap`).
DC contributed content on Gigantum.
ME contributed to the section on processing and deployment to cloud services.
CF wrote paragraphs about \pkg{r-online}, \pkg{dockerfiler}, \pkg{r-ci} and \pkg{r-db}.
LK contributed content on \pkg{dockr}.
SL contributed content on RStudio's usage of Docker.
BM wrote the section on research compendia and made the project Binder ready.
HN \& JN co-wrote the section on the T-Mobile use case.
KR wrote the section about \pkg{holepunch}.
NR wrote paragraphs about shared work environments and GPUs.
LS \& NT wrote the section on Bioconductor.
PS wrote the paragraphs about GitLab CI/CD pipelines with Shinyproxy and OpenFaaS templates.
TS \& JW wrote the section on CyVerse.
CvP wrote the section on the usage of Docker containers in Dodona.
CW wrote the sections on Whole Tale and contributed content about publication reproducibility audits.
NX contributed content on \pkg{liftr}.
All authors approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page} and \href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues} provide details on the respective contributions.

>>>>

The ordering of authors following DN and DE is alphabetical.
DN conceived the article idea, \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}, wrote sections not mentioned below, and revised all sections.
DE wrote the introduction and the section about containerisation and the Rocker Project, and reviewed all sections.
DB wrote the section on \pkg{outsider}.
GD contributed the CARD.com use case.
RC contributed to the section on interfaces for Docker in R (_dynverse_ and `dynwrap`).
DC contributed content on Gigantum.
ME contributed to the section on processing and deployment to cloud services.
CF wrote paragraphs about \pkg{r-online}, \pkg{dockerfiler}, \pkg{r-ci} and \pkg{r-db}.
EH contributed content on \pkg{dockyard}.
LK contributed content on \pkg{dockr}.
SL contributed content on RStudio's usage of Docker.
BM wrote the section on research compendia and made the project Binder-ready.
HN \& JN co-wrote the section on the T-Mobile use case.
KR wrote the section about \pkg{holepunch}.
NR wrote paragraphs about shared work environments and GPUs.
LS \& NT wrote the section on Bioconductor.
PS wrote the paragraphs about GitLab CI/CD pipelines with Shinyproxy and OpenFaaS templates.
TS \& JW wrote the section on CyVerse.
CvP wrote the section on the usage of Docker containers in Dodona.
CW wrote the sections on Whole Tale and contributed content about publication reproducibility audits.
NX contributed content on \pkg{liftr}.
All authors approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page} and \href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues} provide details on the respective contributions.

### 2020-03-12 rockerverse.tex
fix contribution by @thebioengineer
See https://github.com/nuest/rockerverse-paper/issues/26#issuecomment-597935834

The ordering of authors following DN and DE is alphabetical. DN
conceived the article idea,
\href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team},
wrote sections not mentioned below, and revised all sections. DE wrote
the introduction and the section about containerisation and the Rocker
Project, and reviewed all sections. DB wrote the section on
\pkg{outsider}. GD contributed the CARD.com use case. RC \& EH
contributed to the section on interfaces for Docker in R
(\emph{dynverse} and \texttt{dynwrap}). DC contributed content on
Gigantum. ME contributed to the section on processing and deployment to
cloud services. CF wrote paragraphs about \pkg{r-online},
\pkg{dockerfiler}, \pkg{r-ci} and \pkg{r-db}. LK contributed content on
\pkg{dockr}. SL contributed content on RStudio's usage of Docker. BM
wrote the section on research compendia and made the project Binder
ready. HN \& JN co-wrote the section on the T-Mobile use case. KR wrote
the section about \pkg{holepunch}. NR wrote paragraphs about shared work
environments and GPUs. LS \& NT wrote the section on Bioconductor. PS
wrote the paragraphs about GitLab CI/CD pipelines with Shinyproxy and
OpenFaaS templates. TS \& JW wrote the section on CyVerse. CvP wrote the
section on the usage of Docker containers in Dodona. CW wrote the
sections on Whole Tale and contributed content about publication
reproducibility audits. NX contributed content on \pkg{liftr}. All
authors approved the final version. This articles was collaboratively
written at
\href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The
\href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page}
and
\href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues}
provide details on the respective contributions.

>>>>

The ordering of authors following DN and DE is alphabetical. DN
conceived the article idea,
\href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team},
wrote sections not mentioned below, and revised all sections. DE wrote
the introduction and the section about containerisation and the Rocker
Project, and reviewed all sections. DB wrote the section on
\pkg{outsider}. GD contributed the CARD.com use case. RC contributed to
the section on interfaces for Docker in R (\emph{dynverse} and
\texttt{dynwrap}). DC contributed content on Gigantum. ME contributed to
the section on processing and deployment to cloud services. CF wrote
paragraphs about \pkg{r-online}, \pkg{dockerfiler}, \pkg{r-ci} and
\pkg{r-db}. EH contributed content on \pkg{dockyard}. LK contributed
content on \pkg{dockr}. SL contributed content on RStudio's usage of
Docker. BM wrote the section on research compendia and made the project
Binder-ready. HN \& JN co-wrote the section on the T-Mobile use case. KR
wrote the section about \pkg{holepunch}. NR wrote paragraphs about
shared work environments and GPUs. LS \& NT wrote the section on
Bioconductor. PS wrote the paragraphs about GitLab CI/CD pipelines with
Shinyproxy and OpenFaaS templates. TS \& JW wrote the section on
CyVerse. CvP wrote the section on the usage of Docker containers in
Dodona. CW wrote the sections on Whole Tale and contributed content
about publication reproducibility audits. NX contributed content on
\pkg{liftr}. All authors approved the final version. This articles was
collaboratively written at
\href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The
\href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page}
and
\href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues}
provide details on the respective contributions.
